---
title: "linreg:QR decomposition with RC class,Group5,20/9/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg:QR decomposition with RC class,Group5,20/9/2021}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
data("iris")
library(ggplot2)
```

```{r setup}
library(lab4Group5)
```
This vignette summaries the various functions in package lab4Group5.

##linreg()

This function should return a object that contains a list that contains variables in the formula,independent variables matrix,dependent variable,regressions coefficients,the fitted values,the residuals,the degrees of freedom,the residual variance,the variance of the regression coefficients,t-values,p-values.
```{r}
linreg_mod <- linreg(Petal.Length~Species, data=iris)
```

##print()

This function should print out the coefficients and coefficient names.
```{r}
linreg_mod$print()
```

##plot()

This function should plot two plots using ggplot2.One plot is Residuals vs Fitted value,the other is Standardized residuals vs Fitted values.
```{r}
linreg_mod$plot()
```

##resid()

This function should return the vector of residuals e.
```{r}
linreg_mod$resid()
```

##pred()

This function should return the predicted values y^.
```{r}
linreg_mod$pred()
```

##coef

This function should return the coefficients as a named vector.
```{r}
linreg_mod$coef()
```

##summary

This function should return a list that contains coefficients with their standard error, t-value and p-value as well as the estimate of^and the degrees of freedom in the model.
```{r}
linreg_mod$summary()
```
